Non-analogues in paleoecological reconstruction

### 2015-08-27 Paper_Markdown.Rmd

Pollen assemblages are widely used for paleoclimatic reconstruction during the Holocene, but this method is also applied to pollen assemblages from the last Glacial period [@bartlein2011pollen, @kaufman2012multi], and earlier [@tarasov2011progress; @brewer2008climate, @cheddadi1998climate].  A particular challenge for climate reconstruction using these much earlier samples is the presence of non-analogue vegetation.  Non-analogue pollen assemblages pose a problem for many reconstruction techniques, these vegetation assemblages may be the result of sets of climate variables that no longer co-exist, ecological conditions resulting from differing rates of species migration (REF) or release from herbivores [@gill2009pleistocene], or as a result of changes in human land use [@goring2015preset].

@@

>>>>

Pollen assemblages are widely used for paleoclimatic reconstruction during the Holocene, but this method is also applied to pollen assemblages from the last Glacial period [@bartlein2011pollen, @kaufman2012multi], and earlier [@tarasov2011progress; @brewer2008climate, @cheddadi1998climate].  A particular challenge for climate reconstruction using these much earlier samples is the presence of non-analogue vegetation.  Non-analogue pollen assemblages pose a problem for many reconstruction techniques, these vegetation assemblages may be the result of sets of climate variables that no longer co-exist, ecological conditions resulting from differing rates of species migration [@huntley1991plants] or release from herbivores [@gill2009pleistocene], or as a result of changes in human land use [@goring2015preset].

@@

For each pollen model and each sample site we calibrated a model to reconstruct T_{jul} using a pool of samples selected by removing all pollen samples closer than an analogue distance that increased from 0 to 1 at a step size of 0.01.  The calibration dataset for each model and each sample, at each exclusion step was then bootstrapped 30 times, sampling with replacement from the available calibration samples, to obtain a variance parameter, along with a mean prediction, bias estimate, root mean squared error of prediction and sample size estimate.  This full procedure reqired 29,254,650 individual calibrated models (although a number failed due to small sample sizes with large analogue exclusion distances).  To facilitate this large number of models, and the significant processing time, we ran the simulations on an Amazon AWS EC2 server as a parallel process using 30 cores.
